Artificial Intelligence Cource Project\\ {\footnotesize CS410 }

### 2018-01-14 paper/Ruijie/report.tex

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\subsubsection{PCA}
Principal components analysis(PCA) aims to perform a linear mapping of the data to a lower-dimensional space in such a way that the variance of the data in the low-dimensional representation is maximized. Suppose we are given data matrix $X$ with size $n\times p$, where n is the quality of sampling and p is the dimension of feature. The PCA algorithm is shown as follow:
\begin{itemize}
\item Normalize the data : $x=x-\sum_i^N x_i$;
\item Calculate the covariance matrix $C=\frac{X^T X}{n-1}$. Then diagonalize it : $C=V L V^T$, where $V$ is the matrix of eigenvectors and $L$ is diagonal matrix with eigenvalues $¦Ë_i$ .
\item Choose $d$ rows ,the sum of whose variance reach some percentage of original variance. The criterion should be followed Eq(\ref{pac_1}).

@@

\subsection{Deep Learing Based Methods}
Deep learning has been shown as a successful machine learning method for a variety of tasks. In our work, we use a deep neural network with fully-connected multilayer structure both on PCA-processed data and on raw data with \textbf{greedy layer-wise pre training}. Besides, we add L2 regularization in each fully-connected layer to avoid overfitting and control the model complexity.
\subsubsection{network structure} Since the features do not have any locality or direct relationship, we don¡¯t use convolutions.\\

@@

\begin{figure}[!ht]
\centering
   \includegraphics[width=0.24\textwidth]{../figs/nn_pca.pdf}
   \includegraphics[width=0.24\textwidth]{../figs/nn_raw.pdf}
   \caption{a.network \romannumeral1;  b, network \romannumeral2}
   \label{nn_1}
\centering
\end{figure}

@@

Furthermore, we employ Dropout to prevent overfit- ting. While training, dropout is implemented by only keep- ing a neuron active with some probability p, or setting it to zero otherwise.

@@

\section{result}
\end{document}

>>>>

% !TEX TS-program = XeLaTeX
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{booktabs} 
\usepackage{subfigure}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\subsubsection{PCA}
Principal components analysis(PCA)\cite{PCA} aims to perform a linear mapping of the data to a lower-dimensional space in such a way that the variance of the data in the low-dimensional representation is maximized. Suppose we are given data matrix $X$ with size $n\times p$, where n is the quality of sampling and p is the dimension of feature. The PCA algorithm is shown as follow:
\begin{itemize}
\item Normalize the data : $x=x-\sum_i^N x_i$;
\item Calculate the covariance matrix $C=\frac{X^T X}{n-1}$. Then diagonalize it : $C=V L V^T$, where $V$ is the matrix of eigenvectors and $L$ is diagonal matrix with eigenvalues $¦Ë_i$ .
\item Choose $d$ rows ,the sum of whose variance reach some percentage of original variance. The criterion should be followed Eq(\ref{pac_1}).

@@

\subsection{Deep Learing Based Methods}
Deep learning\cite{Deeplearning} has been shown as a successful machine learning method for a variety of tasks. In our work, we use a deep neural network with fully-connected multilayer structure both on PCA-processed data and on raw data with \textbf{greedy layer-wise pre training}. Besides, we add L2 regularization in each fully-connected layer to avoid overfitting and control the model complexity.
\subsubsection{network structure} Since the features do not have any locality or direct relationship, we don¡¯t use convolutions.\\

@@

\begin{figure}[!ht]
\centering
   \includegraphics[width=0.24\textwidth]{../figs/nn_pca.pdf}
   \includegraphics[width=0.24\textwidth]{../figs/nn_raw.pdf}
   \caption{a.network \romannumeral1;  b, network \romannumeral2; }
   \label{nn_1}
\centering
\end{figure}

@@

Furthermore, we employ Dropout\cite{Dropout} to prevent overfit- ting. While training, dropout is implemented by only keep- ing a neuron active with some probability p, or setting it to zero otherwise.

@@

\section{experiment}
\subsection{Label Selection} Besides, we visualize the given data with selected labels into 2-D figure using PCA method, which is shown in Fig(\ref{distribution_1}). By observation, data with Bio-7 label, Material-2 label and Disease-16 have clear boundary while it is very hard to identify the data with Sex-2 label in 2-D space.

\begin{figure}[!ht]
\centering
   \includegraphics[width=0.24\textwidth]{../figs/Material-2.pdf}
   \includegraphics[width=0.24\textwidth]{../figs/Sex-2.pdf}
   \includegraphics[width=0.24\textwidth]{../figs/Disease-16.pdf}
   \includegraphics[width=0.24\textwidth]{../figs/Bio-7.pdf}
   \caption{a.Material-2 Distribution;  b, Sex-2 Distribution2; c, Disease-16 Distribution; d,Bio-7 Distribution}
   \label{distribution_1}
\centering
\end{figure}
\section{result}
\subsection{Logistic Regression} 
We apply logistic regression to four task. Besides, we try different regularization method and solver  with different regularization strength C . We want to choose the best parameter settings and compare the preformence of different regularization method and solver. The result with the change of C is shown as Fig(\ref{lr_result1}).It can be seen that the performance of LR did not vary too much with the change of C, which may mean the data distribution is ideal and the  regularization of this model is not necessary.

\begin{figure}[!ht]
\centering
   \includegraphics[width=0.4\textwidth]{../figs/LR_C.pdf}
   \caption{The performance of LR in 4 tasks with different regularization strength.}
   \label{lr_result1}
\centering
\end{figure}

And the best results on 4 tasks with selected parameters is shown in Table(\ref{lr_result2}).

\begin{table}[tbp]
		\centering
		\begin{tabular}{l|cccc}
			\toprule
			{Label Type} & $F_1 (\%)$ & C &solver &penalty \\
			\midrule
			{\textit{MaterialType}}&99.86 & 4 &lbfgs & l2\\
			{\textit{Sex}}		& 94.96 & 0.001    &sag & l2 \\
			{\textit{DiseaseState}}& 95.72 & 0.001 &lbfgs & l2\\
			{\textit{BioSourceType}}& 98.42 & 0.01 &lbfgs & l2\\
			\bottomrule	
		\end{tabular}

		\caption{Best results and parameter settings for Logistic Regression. }
		\label{lr_result2}
	\end{table}

\subsection{Deep Learning based Method}

\subsubsection{ nn on pca-processed data}
At first we try deep neural network on   pca-processed data. The dimension is 500, and the network is shown in Fig{\ref{nn_1}). Besides,  we use L2 regularization and dropout to avoid overfitting. The dropout rate is 0.50. In the end, we use batch normalization in each layer and it greatly improves the performance. The results and selected parameters are shown in Table(\ref{nnpca_result}).

	\begin{table}[tbp]
		\centering
		\begin{tabular}{l|cccc}
			\toprule
			{Label Type} & $F_1 (\%)$ & learning rate &$batch size$  \\
			\midrule
			{\textit{MaterialType}}&99.30 & 0.001 &32\\
			{\textit{Sex}}		& 92.92 & 0.001    &50 \\
			{\textit{DiseaseState}}& 94.38 & 0.001 &32\\
			{\textit{BioSourceType}}& 95.87 & 0.001 &16\\
			\bottomrule	
		\end{tabular}

		\caption{Best results and parameter settings for nn model on pca data. }
		\label{nnpca_result}
	\end{table}

Besides, we visualize the training process of Sex and Bio tasks with the change of learning. It is shown in Fig(\ref{lr_result}), and it can be seen $lr=0.001$ is the best result in four task.

\begin{figure}[!ht]
\centering
   \includegraphics[width=0.24\textwidth]{../figs/lr_acc_bio.pdf}
   \includegraphics[width=0.24\textwidth]{../figs/lr_acc_sex.pdf}
   \includegraphics[width=0.24\textwidth]{../figs/lr_loss_bio.pdf}
   \includegraphics[width=0.24\textwidth]{../figs/lr_loss_sex.pdf}
   \caption{a.accuracy in Bio task;  b, accuracy in Sex task; c, loss in Bio task; d, loss in Sex task}
   \label{lr_result}
\centering
\end{figure}

\subsubsection{ nn on raw data}
To improve the nn' performance, we try deep neural network on  raw data. Because it is a nonlinear classifier, it may solve the relevant of raw data feature by itself. The dimension is 22283, and the network is shown in Fig{\ref{nn_1}). The setting of L2 regularization, dropout and batch normalization is same as the above experiment. But without the proper initialization (e.g. random initialization), the performance is not better than nn above. On the contrary, the accuracy is only at around 70\%, for it is easily influenced by local optimization. So we use greedy layer-wise pre training method to initialize the weights using 3 different neural network (which have the same structure as autoencoder) . Then the performance is improved a lot, besides the train process becoming faster. The best result and seleted parameters is shown in Table({\ref{nnraw_result}).\\

	\begin{table}[tbp]
		\centering
		\begin{tabular}{l|cccc}
			\toprule
			{Label Type} & $F_1 (\%)$ & learning rate &$batch size$  \\
			\midrule
			{\textit{MaterialType}}&99.78 & 0.001 &32\\
			{\textit{Sex}}		& 92.41 & 0.01    &50 \\
			{\textit{DiseaseState}}& 94.37 & 0.001 &32\\
			{\textit{BioSourceType}}& 98.35 & 0.001 &32\\
			\bottomrule	
		\end{tabular}

		\caption{Best results and parameter settings for nn model on raw data. }
		\label{nnraw_result}
	\end{table}

Compared with Table(\ref{nnpca_result}), it can be seen that MaterialType task and BioSourceType task has been improved, but the Sex task and DiseaseState task did not become higher. Besides, there are some differences among the optimal parameters.

\bibliographystyle{plain}
\bibliography{report.bib}
\end{document}
